Total Score

### 2023-02-06 src/MSAtotal_scores.Rmd
exported chart to jpeg

ggplot(data = score_tidy, aes(y = reorder(msa_state, FINAL_owen_SCORE), x = criteria_score)) + 
    geom_col(aes(fill = criteria)) +
  labs(x = "Total Score (Client)",
       y = " ") +
  theme_light() +
  guides(fill=guide_legend(title="Criteria (weighted)")) +
   scale_fill_manual(values = c("palevioletred1","#FDB462",  "gold", "#44AA99", "dodgerblue4", "#BC80BD"),
                     labels=c('Climate Risk', 'CO2 Emissions', 'Electricity', "Finances", "Real Estate", "Landlord Policy"))

>>>>

jpeg(filename = "wt_criteria_client_bar_chart")
ggplot(data = score_tidy, aes(y = reorder(msa_state, FINAL_owen_SCORE), x = criteria_score)) + 
    geom_col(aes(fill = criteria)) +
  labs(x = "Total Score (Client)",
       y = " ") +
  theme_bw() +
  guides(fill=guide_legend(title="Criteria (weighted)")) +
   scale_fill_manual(values = c("palevioletred1","#FDB462",  "gold", "#44AA99", "dodgerblue4", "#BC80BD"),
                     labels=c('Climate Risk', 'CO2 Emissions', 'Electricity', "Finances", "Real Estate", "Landlord Policy")) +
  scale_x_continuous(limits = c(0, 0.7), expand = c(0,0), breaks=seq(0, 0.7, 0.1))
dev.off()
```
